\lhead{Introduction\hfill Study Paper, Burghard}
\section{Introduction} \label{sec: Introduction}
Investors face a familiar dilemma: They can choose diversified investment funds or spend significant time managing individual stocks. When investing in a single company, one must track news, review their financial statements, and stay informed about the industry. While trading individual stocks offers greater profit potential, it demands substantial time for research and staying current.
\subsection{Motivation and Objectives}\label{sec: Motivation and Objectives}
This project aims to address the previously mentioned issue by developing a program that can predict stock performance without requiring manual user input. Similar to an investment advisor, the program can provide information such as:\\
\\
\textit{\grqq Considering today's data, the stock is likely to rise tomorrow. The price will be 5\% higher than today\grqq{}}\\
\\
The user can then decide whether to buy or sell stocks based on the program's advice.
The goal is reached if the investor will get 1\% better results trading the stock with the program compared to holding the stock in the long term.\\
\\
The project is divided into two parts. While the first part mainly focuses on scientific research regarding the state of the art, the second part will be the implementation of the prediction model.
\subsection{Delimitation}\label{sec: Delimitation}
The program cannot execute trades as it lacks a connection to a broker. Its sole purpose is to provide advice to the user. Additionally, it is designed for a specific stock, which will be chosen at a later point in time. The program won't have a user interface except the console and won't be usable by layman. The work is focused on scientific research about the methods and technologies that are possible to use.