\clearpage
\lhead{Conclusion\hfill Study Paper, Burghard}
\section{Conclusion and Outlook} \label{sec: ConclusionOutlook}

The stored data will be collected till the second part of the project starts in five months. Training data will then be available for almost six months(=180 data-points). An analysis will be conducted on all folders, gathering data to compile into a comprehensive \ac{CSV} file as specified in the morphological box. To address the intermittent data gaps, a linear interpolation will be implemented between consecutive points to mitigate abrupt data variations. Subsequently, an evaluation of the daily news using \ac{FinBERT} will generate news scores across various topics. The overarching goal encompasses creating a substantial dataset wherein each day constitutes a distinct data point inclusive of all samples. Financial ratios will be derived from this dataset, followed by training an \ac{LSTM} \ac{RNN} model to forecast stock prices at varying future intervals, such as one day, one week, and one month ahead.\\
\\
In the realm of \ac{AI}, having quality training data stands out as the most crucial step, and currently, that cornerstone is under construction having the \ac{Pi} running every day to collect data. Alongside this, meticulous planning of methodologies and gaining a comprehensive overview of the literature has been pivotal. This process sets the stage for a deeper exploration of the subject and provides a clear direction for steering the project towards its intended goals.