\lhead{Abstract\hfill Study Paper, Burghard}
\section*{Abstract}\label{sec: Abstract}

A project is underway to tackle a common challenge faced by investors: The choice between diversifying their investments or dedicating significant time to researching individual stocks. The objective is to create a program capable of autonomously predicting stock movements and offering insights to users. This allows users to make informed decisions about buying or selling stocks based on these predictions.\\
The project plan includes the collection of various parameters that affect stock movements, such as news, financial reports, interest rates, global events and economic indicators. The data will be collected from the internet to train an \ac{AI} model. The program will then predict stock movements based on these parameters using real-time inputs.\\
\\
Building on the fundamentals provided by previous research, the bulk of this paper consists of investigating the methods and programs to be used in the second part. This part of the project aims to collect the necessary data to provide a basis for the second part.

To collect the required data autonomously, a \ac{Pi} is set up as a server that automatically executes a program once every day. The data is then stored in folders and backed up on a \ac{SSD}.
Using this data, an \ac{AI} is trained in the following part to predict upcoming stock movements.\\
\\
This project aims to bridge the gap between informed investing and efficient time management for stock market enthusiasts by harnessing the power of \ac{AI} and data analytics.
\newpage